Accelerated convergence of convective simulations using boundary value problems

### 2018-01-11 tex/bvp_paper.tex
figure improvements, figure caption updates

\section{To Do}
\begin{enumerate}
\item Get 3D cases in
\item Continue Improving Figures
\item Write figure captions
\end{enumerate}

@@

\subsection{The Boundary Value Problem}
\begin{figure}[t]
\includegraphics[width=\textwidth]{./figs/time_trace.png}
\caption{Traces of system energies vs. time for a long thermal rundown (a) and BVP convergence
(b) are shown for Ra = $1.30 \cdot 10^7$ ($S = 10^4$).  The two plots are scaled such that
one time unit on the x-axis of either run takes up an equivalent amount of space on the paper
to illustrate the time savings of the BVP run.  (c\&d) Flux plots, where black is the sum of the
flux, blue is enthalphy flux and red is condcutive flux. (c) Fluxes are shown for the IVP at an early
time to illustrate the asymmetry of the flux through the system. (d) Fluxes through the converged,
rundown state are compared to the fluxes in the converged BVP solution, where their difference
is shown in (e). \label{fig:time_trace} }
\end{figure}

@@

\begin{figure}[t]
\includegraphics[width=\textwidth]{./figs/pdf_comparison.png}
\caption{We compare the time-variant dynamics in our 2D solutions by showing probability distribution
functions of the values of vertical velocity (a), horizontal velocity (b), and nonlinear heat
transport (c) in our converged solutions.  The horizontal velocities are very similar, with a
KS test similarity of X.  The vertical velocities, too, are similar, with a KS similarity of
Y.  The nonlinear heat transport, while overall quite similar, shows that the BVP experiences
a greater number of extreme events.  The peak around zero for all three PDFs reflects the
no-slip boundary conditions.\label{fig:pdf_comparison} }
\end{figure}

\begin{figure}[t]
\includegraphics[width=\textwidth]{./figs/temp_comparison.png}
\caption{Here we compare the evolved thermodynamic state of a BVP to that of a rundown IVP that
has been run through a thermal timescale.  (a) The temperature profiles, as a function of height,
are shown. (b) The percentage difference between the temperature profiles, as a function of height,
is shown.  (c) PDFs comparing the values of the point-by-point temperatures over the averaging
window.  While the median of the PDF has a distinct offset between the two runs, the
thermal fluctuations about the mean which drive the convection are nearly the same.
\label{fig:temp_comparison} }
\end{figure}

\begin{figure}[t]
\includegraphics[width=\textwidth]{./figs/parameter_space_comparison.png}
\caption{Here we demonstrate the efficacy of the BVP method at many values of Ra.  We show
(a) Nusselt number scaling, (b) Reynolds number scaling, and (c) scaling of the mean temperature
over the whole simulation.  (a) The Nusselt number follows a classic 2/7 scaling law
\cite{johnston&doering2009}, until it reaches S = $10^{3 + 2/3}$, at which point the
two-roll solution begins oscillating horizontally, showing time-variant Nu.  The range of Nu
over the averaging window is (blah), and the trend of Nu (the variance of the mean Nu) is shown
as (blah).  (b) Re follows an expected 1/2 scaling law. (c) The mean value of temperature, minus
the value at the fixed-temperature boundary, is shown.  As Ra increases, the boundary layers shrink,
and the convection becomes more efficient, we anticipate this value to get closer and closer to
zero as the atmosphere approaches the isotherm defined by the upper boundary.
\label{fig:parameter_space_comparison} }
\end{figure}

>>>>

@@

\subsection{The Boundary Value Problem}
\begin{figure}[t]
\includegraphics[width=\textwidth]{./figs/time_trace.png}
\caption{Traces of system energies vs. time for a long thermal rundown (a) and BVP convergence
(b) are shown for Ra = $1.30 \cdot 10^8$ ($S = 10^5$).  The horizontal extent of the subplots is set
such that one simulation time unit takes up an equal amount of paper space in (a) and (b).
The dashed vertical line on (a) represents the time at which the BVP is solved on the run in (b),
and the horizontal dashed lines show the equilibrium value of the energies.
(c) System fluxes early in the run (the orange highlights in (a)).  Black is the sum of the flux, purple
is the convective flux, and red is the conductive flux.
(d) Fluxes in the converged rundown IVP compared to the ``converged'' BVP.  The sum of flux is shown in
black \& grey, the convective flux is shown in purple \& pink, and the conductive flux is shown in red \& orange.
(e) The differences between the BVP and rundown fluxes is shown.  While not in perfect agreement, the BVP fluxes
are much closer to the converged state than the initial fluxes, as in (c).
\label{fig:time_trace} }
\end{figure}

@@

\begin{figure}[t]
\includegraphics[width=\textwidth]{./figs/pdf_comparison.png}
\caption{Frequency distribution functions of the vertical velocity (a), horizontal velocity (b), and nonlinear
vertical transport (c) are shown for a 2D run at $S = 10^5$.  We sample flows every 0.1 time units for 500 freefall
times, and include the flows at all points on the grid at each of these samples in these distributions.  All
distributions are biased by the no-slip, impenetrable boundary conditions, coupled with the dense spacing of our
Chebyshev grids near the boundaries, so there is a large peak around zero. The distributions, and thus the nonlinear
dynamics, are broadly similar, but they do not pass a two-tailed Kolmogorov-Smirnov similarity test. (NOTE TO
CO-AUTHORS: I NEED TO THINK BETTER ON HOW TO COMPARE PDFS, IF YOU HAVE IDEAS PLEASE SEND THEM)
\label{fig:pdf_comparison} }
\end{figure}

\begin{figure}[t]
\includegraphics[width=\textwidth]{./figs/temp_comparison.png}
\caption{Comparisons of the evolved thermodynamic states of a BVP solution and a long IVP rundown at
$S = 10^5$ are shown.  (a) Evolved temperature profiles, as a function of height.
(b) The percentage difference between the temperature profiles (as shown in (a)), as a function of height.
(c) Frequency distributions, as in Fig. \ref{fig:pdf_comparison},
comparing the values of the point-by-point temperatures over the averaging
window. The mode of the frequency distribution has a distinct offset between the two runs due to
the clear difference between the profiles in (a), but the
thermal fluctuations about the mean which drive the convection are similar (AS IN FIG. \ref{fig:pdf_comparison},
I NEED TO THINK MORE ON THE PDF COMPARISON).
\label{fig:temp_comparison} }
\end{figure}

\begin{figure}[t]
\includegraphics[width=\textwidth]{./figs/parameter_space_comparison.png}
\caption{Compensated scaling plots are shown for the Nusselt number (a), the
Reynolds number (b), and the volume-averaged temperature (c).  All plots are linear(y)-log(x),
and any differences vertically are generally small.  Symbols represent the mean value of
a measurement, vertical lines represent the standard deviation of the measurement over the
time window, and error bars represent the shift in the mean value over the window.
(a) Nu, which measures heat transport, scales roughly like $Ra^{1/5}$, and above Ra$\geq 10^6$,
simulations display horizontally oscillating plumes which have oscillating periods of high transport
and low transport.  The mean value is marginally diminished as a result, and the range of Nu over time
is large. (b) Re, which measures the level of turbulence in the evolved solution, scales as
Ra$^{0.45}$ in 2D and (something else) in 3D. (c) The average temperature flucutation, minus the top
temperature, gives us a measure of the extent of the upper boundary, and is in some ways a more stationary
proxy for Nu, and it displays similar scaling.  The temperature profile is slow to adjust, and differences between
BVP solutions and rundown solutions are easier to pick out.
\label{fig:parameter_space_comparison} }
\end{figure}
